
## Insights (cards)

```{r, include=FALSE}
# Set up template page per organisation
# if (is.na(meta_params$organisation) | length(meta_params$organisation) > 1) {
#   meta_params$organisation <- "Overall"}
org_summary <- list()
#  --- Filter data to organisation
org_summary$data <- map(summary$data,
                   ~ .x |> filter(organisation == meta_params$organisation))
# --- print-ready tables
org_summary$tables <- summary$tables[[meta_params$organisation]]
# overall data
key_insights_data <- map(org_summary$data,
                        ~ .x |> filter(strata == "overall"))

# Create key insights text
key_text <- generate_key_insights(key_insights_data$latest)
meta_params$strata <- "sex"
```

::: {.card title="Key insights" fill=false}
- **`r key_text$n_id` participants** contributing data
  - `r key_text$n_followup` participants are continuing to report ongoing weight measurements
- **`r key_text[["weight_change_percent_prewar"]]` loss of bodyweight**^[Median and interquartile range (25%-75% of participants)] from pre-war to latest measurement, equivalent to 
  - A median weight loss of `r key_text[["weight_change_unit_prewar"]]`
  - A drop in BMI by `r key_text[["bmi_change_unit_prewar"]]`
- **`r key_text[["bmi_category_daily_Underweight"]]` participants clinically underweight**^[WHO classification: underweight body mass index of < 18.5], compared to `r key_text[["bmi_category_prewar_Underweight"]]` pre-war
:::

```{r, out.width="100%"}
#| title: "BMI classification"
#| fill: false
org_summary$tables$bmi_crosstab
markdown("<details> <summary> About the data </summary> 
         Prevalence of body mass index (BMI) classifications among participants, calculated from self-reported weight before October 2023 (pre-war), and latest measurement during study period (from July 2025). Adult BMI classifications are underweight (under 18.5 kg/m2), normal weight (18.5 to 24.9), overweight (25 to 29.9), and obese (30 or more).")
```

## Participation (tabs)

::: {.panel-tabset}

### Participation
```{r, out.height="100%"}
#| fill: false
#| fig-align: center
plot_participants_over_time(key_insights_data$timeseries) |> 
  ggplotly()
markdown("<details> <summary> About the data </summary> 
         Daily participation from newly recruited participants (light green), or repeat measurements from returning participants (dark blue); with cumulative number of unique participants over time (shaded grey area) and their unique measurements (grey line). </details>")
```

### Baseline
```{r}
#| fill: false
org_summary$tables$demographic_strata
```

### Data
```{r}
#| fill: false
org_summary$tables$data_quality
```
:::

## Demographic strata

::: {.panel-tabset}

### Overall 

{{< include _tab-strata.qmd >}}


### Sex

{{< include _tab-strata.qmd >}}


### Age

{{< include _tab-strata.qmd >}}

:::
