<!-- Organisation-level data -->

```{r, include=FALSE}
## Load Data
data_filtered <- data |> 
  filter(organisation == params$organisation)
# split data into summary by recent 72h, or by daily cross-section
data_filtered_current <- data_filtered |> 
  filter(is.na(date))
data_filtered_timeseries <- data_filtered |> 
  filter(!is.na(date))

insights <- generate_key_insights(data_filtered_current, 
                                  strata = "overall")
```

::: {.callout-tip collapse="false" title="Key insights"}
- Data updated as of **`r insights$latest_date`**
- Recent data from **`r insights$cohort_size_current` participants** (**`r insights$cohort_percent_currently_participating`%** of all enrolled participants)
- Median change of **`r insights$median_change`%** compared to pre-war weight (with a typical range of `r insights$lower_change`% to `r insights$upper_change`%)
:::

::: {.callout-tip collapse="false" title="Nutritional status"}

::: {.panel-tabset} 

### Weight change

::: {.panel-tabset} 

#### Current status

```{r}
weight_variable <- "weight_percent_change_prewar"
data_filtered_current_weight <- data_filtered_current |> 
  filter(variable == weight_variable) |> 
  pivot_wider(names_from = stat, values_from = value) 

w_kg <- data_filtered_current_weight |> 
  filter(group %in% c("sex", "agegroup", "governorate", "children_feeding")) |> 
  mutate(group = as.character(group)) |> 
  highlight_key(~ group) 

w_kg_plot <- w_kg |> 
  ggplot(aes(y = group, group = group)) +
  geom_point(aes(x = median, shape = group, col = label),
             position = position_dodge(width = 0.5), 
             show.legend = F, size = 3) +
    geom_linerange(aes(xmin = q1, xmax = q3,
                       col = label),
             position = position_dodge(width = 0.5), 
             show.legend = F, linewidth = 3, alpha = 0.8)

w_kg_plot <- ggplotly(w_kg_plot) |> 
   highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE)

w_kg_plot
```

Summary of most recent data provided by participants reporting over the last 3 days. Current weight in kilograms (kg) and BMI (body mass index), in addition to percent change in weight and BMI from pre-war levels (before October 8th 2023) are shown on the x-axes of the panels. Negative values of percent change indicate weight loss, i.e. ‘-20%’ indicates an average loss of 20% of weight or BMI.

#### Trends over time

TBD

:::

<!--- close weight tab --->

### BMI

::: {.panel-tabset}

#### Overall

```{r}
print("plot overall BMI")
```

#### By demographic

a plot here

::: 

:::

:::
