```{r include=FALSE}
key_insights_data <- map(org_summary$data,
                        ~ .x |> filter(strata == "overall"))

# Create key insights text
key_text <- generate_key_insights(key_insights_data$latest)
```

::: {.card title="Key insights" fill=false}
- **`r key_text$n_id` participants** contributing data
  - `r key_text$n_followup` participants are continuing to report ongoing weight measurements
- **`r key_text[["weight_change_percent_prewar"]]` loss of bodyweight**^[Median and interquartile range (25%-75% of participants)] from pre-war to latest measurement, equivalent to 
  - A median weight loss of `r key_text[["weight_change_unit_prewar"]]`
  - A drop in BMI by `r key_text[["bmi_change_unit_prewar"]]`
- **`r key_text[["bmi_category_daily_Underweight"]]` participants clinically underweight**^[WHO classification: underweight body mass index of < 18.5], compared to `r key_text[["bmi_category_prewar_Underweight"]]` pre-war
:::

```{r, out.width="100%"}
#| title: "BMI classification"
#| fill: false
org_summary$tables$bmi_crosstab
markdown("<details> <summary> About the data </summary> 
         Prevalence of body mass index (BMI) classifications among participants, calculated from self-reported weight before October 2023 (pre-war), and latest measurement during study period (from July 2025). Adult BMI classifications are underweight (under 18.5 kg/m2), normal weight (18.5 to 24.9), overweight (25 to 29.9), and obese (30 or more).")
```


