---
title: ""
format: 
  html:
    include-in-header:
      text: |
            <script src="lshtm.js"></script>
    css: "styles.css"
    fig-format: svg
    page-layout: custom
    anchor-sections: true
    smooth-scroll: true
toc: false
execute: 
  echo: false
---

<!-- Setup, no output -->

```{r setup, include=FALSE}
## Packages
pacman::p_load(here, 
               purrr, readr, dplyr,
               bslib, bsicons, 
               ggplot2, plotly)

## Load data dictionary
datadict <- readRDS("data/data_dictionary.RDS")

## Load Data RDS
data <- readRDS("data/public/summary-stats.RDS")
data <- list_rbind(map(data, ~ list_rbind(.x))) |> 
  filter(!grepl("-", group))

params <- list("organisation" = NULL,
               "strata" = c("overall", 
                            "sex", "agegroup", "governorate", "role", "children_feeding"))

## Source plotting scripts
source(here("R", "data-analysis/generate_key_insights.R"))
source(here("R", "data-analysis/recode_data_table.R"))
source(here("R", "data-analysis/plot_participants_over_time.R"))
source(here("R", "data-analysis/plot_current_summary_stats.R"))
source(here("R", "data-analysis/plot_time_series_statistics.R"))
source(here("R", "data-analysis/plot_bmicategory_proportions_time_series.R"))
source(here("R", "data-analysis/ggplot_theme.R"))
```

<!-- Global sidebar -->

:::: {.columns}

::: {.column width="25%"}

::: {.callout-note collapse="false" title="Dashboard"}
This project provides real-time information on the **nutritional status of humanitarian staff in Gaza**. Our aim is to inform humanitarian decision-making, advocacy, and diplomatic action to improve the lives of the affected population. We are developing this project during a rapidly changing situation: **please interpret results with caution**.

[**Read more**](./about){.btn .btn-outline-primary .btn role="button"} 
:::

::: {.callout-caution collapse="false" title="Join us"}
We are actively seeking participants to support the project, and welcome humanitarian staff to get in touch. 

[**Join us**](./contact){.btn .btn-outline-success .btn role="button"} 
:::

:::


::: {.column width="75%"}

::: {.panel-tabset}

## **All participants**

```{r}
params$organisation <- "all"
```

{{< include _organisation.qmd >}}


## **UNRW**

```{r}
params$organisation <- "UNRW"
```

{{< include _organisation.qmd >}}

## **Save the Children International**

```{r}
params$organisation <- "SCI"
```

{{< include _organisation.qmd >}}

:::

:::

::::
