---
title: ""
format: 
  dashboard:
    orientation: columns
    css: "styles.css"
    fig-format: svg
    anchor-sections: true
    scrolling: false
lightbox: true
execute: 
  echo: false
  cache: true
---

<!-- Setup -->

```{r setup, include=FALSE}
## Packages
pacman::p_load(here, 
               purrr, readr, dplyr,
               bslib, bsicons, 
               ggplot2, plotly, shiny)
## Source plotting scripts
source(here("R", "data-analysis/generate_key_insights.R"))
source(here("R", "data-analysis/recode_data_table.R"))
source(here("R", "data-analysis/plot_participants_over_time.R"))
source(here("R", "data-analysis/plot_current_summary_stats.R"))
source(here("R", "data-analysis/plot_time_series_statistics.R"))
source(here("R", "data-analysis/plot_bmicategory_proportions_time_series.R"))
source(here("R", "data-analysis/ggplot_theme.R"))

## Load data ----------------------------------
datadict <- readRDS("data/data_dictionary.RDS")
data <- readRDS("data/public/summary-stats.RDS")
data <- list_rbind(map(data, ~ list_rbind(.x))) |>
  filter(!grepl("-", group)) |> 
  filter(!grepl("other", sex))
## Set parameters -----------------------------
params_meta <- list("organisation" = "all", # set to "all" by default
               "strata" = c("Overall", 
                            "sex", "agegroup", "governorate", "role",
                            "children_feeding"))
# remove!
overall <- data |> 
  filter(group == "overall" & organisation == "all")
```

<!-- Global sidebar ---------------------------------------------------------->
## {.sidebar}

This project provides real-time information on the **nutritional status of humanitarian staff in Gaza**. 
Our aim is to inform humanitarian decision-making, advocacy, and diplomatic action to improve the lives of the affected population. 

We invite all humanitarian staff to participate in the project - please consider [**joining us**](./contact).

We are developing this project during a rapidly changing situation: interpret results with caution.

[**About the project**](./about){.btn .btn-info .btn role="button"} 


<!-- Top level pages --------------------------------------------------------->

# All participants

```{r include=FALSE}
params_meta$organisation <- "all"
```

{{< include quarto/_organisation.qmd >}}

# UNRWA

```{r include=FALSE}
#params_meta$organisation <- "UNRWA"
```

<!--{{< include quarto/_organisation.qmd >}}-->

# Save the Children International

```{r include=FALSE}
params_meta$organisation <- "Save the Children International"
```

{{< include quarto/_organisation.qmd >}}




<!-- javascript to set the default plot to Overall -->
```{js}
$(document).ready(function() {
    document.getElementById("filter").getElementsByClassName("selectized")[0].selectize.setValue("overall", false);
});
```
