

::: {layout="[[1,1,1], [1], [1]]" class = "no-box" data-panel-expand="false"}

```{r}
value_box(
  title = "Clinically underweight",
  value = key_text[["bmi_category_daily_Underweight"]],
  p("BMI < 18.5"),
  theme = "warning"
)
```

```{r}
value_box(
  title = "Bodyweight loss since 2023",
  value = key_text[["weight_change_percent_prewar"]],
  p("Median (25%-75%)"),
  theme = "info"
) 
```

```{r}
value_box(
  title = "Participants",
  value = key_text$n_id,
  p(key_text$n_followup, "providing ongoing updates"),
  theme = "success"
) 
```
:::

This project provides real-time information on the nutritional status of humanitarian staff in Gaza by tracking changes in weight and [Body Mass Index (BMI)](https://www.who.int/data/gho/data/themes/topics/topic-details/GHO/body-mass-index). Our aim is to inform humanitarian decision-making, advocacy, and diplomatic action to improve the lives of the affected population.These key insights are calculated using data from all participants from a selected organisation (or overall, if the 'All Participants' tab is selected). For further information on data generation and quality please see the [Study Protocol](./protocol) and the Participation tab.

<h2 style="color: #2c3e50; margin-bottom: 1rem;">
  Change in Body Mass Index (BMI) from pre-war
</h2>

The below plot compares the proportion of the surveyed population that falls into each WHO BMI category (underweight, normal, overweight, obese) from pre-war (2023) to currently.

::: {.panel layout-nrow=2 height="80%" class = "no-box"}

```{r}
#| layout-ncol: 2
#| fill: false

plot_data_latest <- org_summary$data$latest |> 
  filter(strata == "overall") |> 
  mutate(Stratum = fct_drop(Stratum))
plot_bmi_categories(plot_data = plot_data_latest) |> 
  ggplotly(tooltip = c("fill", "y", "x")) |> 
  layout(legend = list(orientation = "h"))

org_summary$tables$bmi_crosstab
```

<details><summary>About the data</summary>The percentage of participants by BMI classification^[Body Mass Index: a standardised measure of weight-for-height, in kilograms per metre squared]. Showing all participants' pre-war BMI^[Calculated from estimated weight in October 2023, self-reported at study enrollment], and the most recent ('current') measurement from each participant since the study began in July 2025. Underweight BMI classification (<18.5kg/m2) shown in yellow; with light to dark green, showing normal weight range (18.5-24.9kg/m2), overweight (25 to 29.9kg/m2), and obese (over 30kg/m2) classifications.</details>

:::
