```{r, include=FALSE}
# Set up template per organisation
org_summary <- list()
# --- Filter data to organisation
org_summary$data <- map(summary$data,
                   ~ .x |> filter(organisation == meta_params$organisation))
org_summary$tables <- summary$tables[[meta_params$organisation]]
# key insights
key_insights_data <- map(org_summary$data,
                        ~ .x |> filter(strata == "overall"))
key_text <- generate_key_insights(key_insights_data$latest)
para <- markdown('- **`r key_text[["weight_change_percent_prewar"]]` loss of bodyweight**^[Median and interquartile range (25%-75% of participants)] from pre-war to latest measurement, equivalent to 
  - A median weight loss of `r key_text[["weight_change_unit_prewar"]]`
  - A drop in BMI by `r key_text[["bmi_change_unit_prewar"]]`
  
- **`r key_text[["bmi_category_daily_Underweight"]]` participants clinically underweight**^[WHO classification: underweight body mass index of < 18.5], compared to `r key_text[["bmi_category_prewar_Underweight"]]` pre-war
:::')
```

::: {.panel-tabset} 

<!-- tab 1. key insights -->

### Key insights

{{< include quarto/_key-insights.qmd >}}

<!-- tab 2. demographic strata -->

### Trends by demographic

::: {.panel-tabset}

#### Overall 

```{r}
meta_params$strata <- "overall"
```

This tab shows overall results for this organisation.

{{< include quarto/_tab-strata.qmd >}}

#### Sex

```{r}
meta_params$strata <- "sex"
```

This tab shows results stratified by biological sex as declared by participants (male/female/prefer not to answer).

{{< include quarto/_tab-strata.qmd >}}

#### Age

```{r}
meta_params$strata <- "age"
```

This tab shows results stratified by age (<30 years old, 30-45 years old, >45 years old).

{{< include quarto/_tab-strata.qmd >}}

#### Dependents

```{r}
meta_params$strata <- "children_feeding"
```

This tab shows results stratified by the number of minor dependents under the care of the participant.

{{< include quarto/_tab-strata.qmd >}}

#### Staff role

```{r}
meta_params$strata <- "role"
```

This tab shows results stratified by humanitarian staff role.

{{< include quarto/_tab-strata.qmd >}}

#### Location

```{r}
meta_params$strata <- "governorate"
```

This tab shows results stratified by location, using Gaza governorates.
{{< include quarto/_tab-strata.qmd >}}

:::

<!--- tab 3. participants + data quality -->

### Participation

{{< include quarto/_participation.qmd >}}

:::
