
#### BMI categories

##### {width="70%"}

```{r, results='asis'}
#| title: "Pre-war to now"
print(log$tab_bmi_categories[[meta_params$organisation]])
```

##### {width="30%"}

::: {.card .bmi_cat_card .lshtm_widget fill="false" title="BMI category % by week"}
<div class="lshtm_widget_identifier" id="bmi_cat">
```{r, results="asis"}
#| fig-align: center
for(i in strata) {
  visible_class = ifelse(i == strata[1], "visible", "")
  cat(glue::glue("<div class='lshtm_widget_content {visible_class}' id='bmi_cat_{i}'>"))
  print(
     plot_bmicategory_proportions_time_series(
     summary_daily_org,
     strata = i
    )
  )
  cat('</div>')
}
```
</div>
:::

#### Weight and BMI

##### column

::: {.card .weight_trend_card .lshtm_widget fill="false"}
<div class="lshtm_widget_identifier" id="weight_trend">
```{r, results="asis"}
#| fig-align: center
for(i in strata) {
  visible_class = ifelse(i == strata[1], "visible", "")
  cat(glue::glue("<div class='lshtm_widget_content {visible_class}' id='weight_trend_{i}'>"))
  print(
   plot_time_series_statistics(
      summary_daily_org,
      #summary_variable = "weight",
      strata = i
    ) +
  plot_time_series_statistics(
      summary_daily_org,
      #summary_variable = "weight_change_percent_prewar",
      strata = i
    ) +
     plot_layout(ncol = 2)
  )
  cat('</div>')
}
```
</div>
:::

##### column

::: {.card .bmi_trend_card .lshtm_widget fill="false"}
<div class="lshtm_widget_identifier" id="bmi_trend">
```{r, results="asis"}
#| fig-align: center
for(i in strata) {
  visible_class = ifelse(i == strata[1], "visible", "")
  cat(glue::glue("<div class='lshtm_widget_content {visible_class}' id='bmi_trend_{i}'>"))
  print(
   plot_time_series_statistics(
      summary_daily_org,
      #summary_variable = "bmi",
      strata = i
    ) +
  plot_time_series_statistics(
      summary_daily_org,
      #summary_variable = "bmi_change_percent_prewar",
      strata = i
    ) +
     plot_layout(ncol = 2)
  )
  cat('</div>')
}
```
</div>
:::

####

::: {.callout-note collapse="true" appearance="minimal"}
Trends over time in participant current measurements, with comparison to pre-war levels (% change since October 2023), since the beginning of the project. BMI by WHO category: underweight <18.5, normal 18.50 – 24.99, overweight ≥ 25, obese ≥ 30. Calculated as the number of measurements per week that fall in each category, divided by the total number of measurements that week ("N").
:::

