```{r include=FALSE}
# Create key insights text
key_text <- generate_key_insights(org_summary$data$latest_records, strata = "overall")
```

####

##### {width="20%"}

::: {.card title="Key insights"}
- Data contributed by **`r key_text$cohort_n` participants** over `r key_text$date_range`^[All participants reported at baseline, with `r key_text$cohort_fup` participants reporting repeated measurements in follow up]
- Since **October 2023**, median weight change of **`r key_text$median_iqr`%**^[Self reported weight before the war compared to latest weight measured in study]
- `r key_text$cohort_underwt_pc` participants with **underweight** body mass index, compared to `r key_text$cohort_underwt_pc_prewar` before October 2023^[WHO category for underweight BMI of < 18.5]
:::

##### 

::: {.card_sidebar}
Median and 25-75% range of participant weight in kilograms (kg) and [Body Mass Index](https://www.cdc.gov/bmi/adult-calculator/index.html?), with % change from pre-October 2023. Negative % indicates weight loss.
:::
```{r}
#| title: "Current summary"
#| fig-align: center
plot_current_summary_stats(org_summary$data$latest_records, strata = "overall")
```

##### 

::: {.card_sidebar}
Daily participation, count of weight measurements contributed by: newly recruited participants (green); measurements from previously enrolled participants (blue); or, previously enrolled participants without new data (grey, lost to follow up).
:::
```{r}
#| fig-align: center
plot_participants_over_time(org_summary$data$daily_records, strata = "overall") |> 
  ggplotly()
```

##### 

```{r}
#| content: "card-sidebar"
```

```{r}
#| title: "Change in BMI category"
org_summary$tables$bmi_crosstab
```
