```{r include=FALSE}
# Create key insights text
key_text <- generate_key_insights(summary_all_org[["overall"]])
```

####

##### {width="20%"}

::: {.card}
- Data contributed by **`r key_text$cohort_n` participants** over `r key_text$date_range`^[All participants reported at baseline, with `r key_text$cohort_fup` participants reporting repeated measurements in follow up]
- Since **October 2023**, median weight change of **`r key_text$median_iqr`%**^[Self reported weight before the war compared to latest weight measured in study]
- `r key_text$cohort_underwt_pc` participants with **underweight** body mass index, compared to `r key_text$cohort_underwt_pc_prewar` before October 2023^[WHO category for underweight BMI of < 18.5]
:::

##### 

::: {.card .current_summary_card .lshtm_widget title="Current summary" fill="false"}
<div class="lshtm_widget_identifier" id="current_summary">
```{r, results="asis"}
#| fig-align: center
for(i in strata) {
  # show the first stratum (overall) by default
  visible_class = ifelse(i == strata[1], "visible", "")
  cat(glue::glue("<div class='lshtm_widget_content {visible_class}' id='current_summary_{i}'>"))
  print(
    plot_current_summary_stats(
      summary_all_org,
      strata = i
    )
  )
  cat('</div>')
}
```
</div>
:::

::: {.card .participants_card .lshtm_widget fill="false"}
<div class="lshtm_widget_identifier" id="participants">
```{r, results="asis"}
#| fig-align: center
for(i in strata) {
  visible_class = ifelse(i == strata[1], "visible", "")
  cat(glue::glue("<div class='lshtm_widget_content {visible_class}' id='participants_{i}'>"))
  print(
    plot_participants_over_time(
      summary_daily_org,
      strata = i
    )
  )
  cat('</div>')
}
```
</div>
:::

##### 

```{r}
#| title: "Change in BMI category"
summary_tables_org$bmi_crosstab
```

#### {height="15%"}

::: {.callout-note collapse="true" title="Data" appearance="simple"}
Summary ranges:
- Median and 25-75% range of participant weight in kilograms (kg) and [Body Mass Index](https://www.cdc.gov/bmi/adult-calculator/index.html?), with % change from pre-October 2023. Negative % indicate weight loss.

Daily participation:
- Measurements contributed by newly recruited participants ("New")
- Measurements from previously enrolled participants ("Repeated")
- Enrolled participants measured at baseline only ("Lost to follow up")
:::
